---
title: "business_forecasting_assignment06"
author: "Adwait Kalsekar"
date: "2023-11-21"
output: html_document
---

# ARIMA Model

### Importing Libraries
```{r}
library(fpp)
library(fpp2)
library(forecast)
```

### Reading Dataset
```{r}
df <- read.csv("NJ_HPI.csv")
head(df)
```

### Converting to Time Series
```{r}
df_ts <- ts(df$HPI.NJ, start=c(1975, 1), end=c(2023, 2), frequency=4)
head(df_ts)
```

### Plotting the Time Series
```{r}
plot(df_ts)
```

### Finding Number of differences required for a stationary series
```{r}
ndiffs(df_ts)
```

### Finding Number of differences required for a seasonally stationary series
```{r}
nsdiffs(df_ts)
```

### Plotting ACF and PACF for the Time Series
```{r}
tsdisplay(df_ts)
```

### Setting Diff 1
```{r}
df_ts_diff1 <- diff(df_ts, 1)
plot(df_ts_diff1)
```

### Plotting ACF and PACF for the Time Series with Diff 1
```{r}
tsdisplay(df_ts_diff1)
```

### ARIMA Model
```{r}
df_ts_arima <- auto.arima(df_ts, trace = TRUE, stepwise = FALSE)
df_ts_arima
```

#### Analysis:
> The best model comes out to be ARIMA(3,1,0)(0,0,2)[4] \
> Which is of the form ARIMA(p,d,q)(P,D,Q)[s], where,

* p: The order of the autoregressive (AR) component
* d: The degree of differencing (the number of times the series is differenced to achieve stationarity)
* q: The order of the moving average (MA) component
* P: The seasonal order of the autoregressive component
* D: The seasonal order of differencing
* Q: The seasonal order of the moving average component
* s: The length of the seasonal cycle

> Looking at the Best model, it can be inferred that the model has:

* An autoregressive component of order 3
* A first-order differencing to make the series stationary
* A moving average component of order 0
* A seasonal moving average component of order 2
* A seasonal cycle of length 4

### Residual Analysis
```{r}
Acf(df_ts_arima$residuals)
plot.ts(residuals(df_ts_arima))
hist(df_ts_arima$residuals)
tsdiag(df_ts_arima)
```

#### Interpretation:

> Looking at the residuals we can see that the residuals are normally distributed with mean close to 0. \
> Also the Acf shows no correlation between the residuals. \
> There is no observable pattern in the plot of residuals. \
> Hence, we can confirm that there is no more data to be extracted from the residuals.

### Forecasts from ARIMA Model for next 5 periods
```{r}
attributes(df_ts_arima)
df_ts_arima_forecast <- forecast(df_ts_arima, h=5)
plot(df_ts_arima_forecast)
```

### Accuracy Measures
```{r}
accuracy(df_ts_arima_forecast)
```